NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration

### 2022-08-25 main.tex

\subsection{Water permeation through membranes}
Dependence of water permeation rate through membranes on the membrane properties has been under great interest because
it serves as a proxy for permeation of other hydrophilic molecules such as drugs \cite{??}, and is also relevant in understanding
MRI imaging \cite{??}. Several models for water permeation are formulated based on experiments and simulations predicting
different dependencies on membrane properties but concensus on how water permeability depends on basic membrane properties,
such as area per lipid and thickness, or molecular composition has not yet been reached \cite{shinoda16,venable19,??}.
This is partially because collection of experimental and simulation data for water permeability from membranes with
wide range of properties has been tedious.
Here we demonstrate the power of the NMRlipids databank by analysing how the water permeability through lipid bilayers depend
on area per lipid, thickness and temperature. The results shown in Fig.~\ref{fig:permeability} are calculated by averaging over
all the simulations in the databank with the same variable under interest (area per lipid, thickness or temperature).
%to find correlation between membrane properties is exemplified in Fig.~\ref{??} showing how water diffusion through and along the membrane correlate with different properties of systems. While NMRlipids databank enables similar analyses for any membrane properties, these are selected due to their relevance in the development of MRI imaging methods~\cite{??}.

>>>>

\subsection{Water diffusion anisotropy in membrane systems}
The anisotropy of water diffusion in the direction of membrane surface and through the membrane is utilized in MRI imaging \cite{??} and regulates the drug translocation particularly in skin \cite{hansen13,wen18,nitsche19,roberts21,??}. The importance of membrane properties on the anisotropic diffusion has been recognized and several models linking the water permeation with the membrane properties have been formulated \cite{??}, yet the consensus on how water permeability depends on basic membrane properties, such as area per lipid and thickness, or molecular composition has not yet been reached \cite{nitsche13,nitsche16,shinoda16,venable19,??}. 
This is partially because collection of experimental and simulation data for water permeability from membranes with
wide range of properties has been tedious.
Here we demonstrate the power of the NMRlipids databank by analysing how the water permeability through lipid bilayers depend
on area per lipid, thickness and temperature. The results shown in Fig.~\ref{fig:permeability} are calculated by averaging over
all the simulations in the databank with the same variable under interest (area per lipid, thickness or temperature).
%to find correlation between membrane properties is exemplified in Fig.~\ref{??} showing how water diffusion through and along the membrane correlate with different properties of systems. While NMRlipids databank enables similar analyses for any membrane properties, these are selected due to their relevance in the development of MRI imaging methods~\cite{??}.
